Compilation and Backend-Independent Vectorization for Multi-Party Computation

### 2022-05-01 overleaf/results.tex
wip experiments section

\ishaq{TODO: go through description again, and add why each benchmark may be important from MPC/private-learning/distributed-computing perspective}
\begin{enumerate}
    \item {\em Biometric Matching} Server has a database S of {\tt N} records, each record's dimension is {\tt D}. Client submits a query C, client and server compute the closest record to C in an MPC. We use {\tt N=128} for {\em both} and {\tt N=4096} for {\em vec}. {\tt D} is fixed at 4.

@@

- Discuss Overall LAN results (Time, Communication Size)
- Discuss inner product and biometric in detail on LAN
- Discuss their comparison (Time) with WAN
- Discuss hand simdified code (native MOTION)
- Put error bars

\begin{figure*}[htbp]
\centering
\include{graphs/lan/all-hist-OnlineSetupTimesec}
\caption{Circuit Evaluation Time (Setup + Online) of Benchmarks}
\label{fig:graph_all_online_setup}
\end{figure*}

>>>>

\ishaq{TODO: go through description again, and add why each benchmark may be important from MPC/private-learning/distributed-computing perspective}

\begin{enumerate}
    \item {\em Biometric Matching} Server has a database S of {\tt N} records, each record's dimension is {\tt D}. Client submits a query C, client and server compute the closest record to C in an MPC. We use {\tt N=128} for {\em both} and {\tt N=4096} for {\em vec}. {\tt D} is fixed at 4.

@@

\begin{figure*}[htbp]
\centering
\include{graphs/lan/all-hist-OnlineSetupTimesec}
\caption{Circuit Evaluation Time (Setup + Online) of Benchmarks}
\label{fig:graph_all_eval_time}
\end{figure*}

We show circuit evaluation times in \cref{fig:graph_all_eval_time}. In terms of amenability to vectorization, we divide benchmarks into 3 categories: 1) {\it High:} these include convex hull, cryptonets max pooling, minimal points and private set intersection. These benchmarks are highly parallelizable and see 25x to 70x speedup in BMR, and 30x to 55x in GMW protocol. 2) {\it Medium:} these include biometric matching, DB Variance, histogram, inner product, k-means iteration and MNIST ReLU. These benchmarks have non-parallelizable phases e.g. the summing phase of inner product and biometric matching. Still, most computation is parallelizable and it results in speedup from 5x to 25x in BMR, and 2x to 25x in GMW protocol. 3) {\it Low:} these include the Database Join and the regular expression benchmarks (count 102, count 10, longest 102 and max distance between symbols). There is very little parallelizable computation in these programs, thus the speedup is lower. We see a speedup from 1.1x to 2x in BMR. In GMW, DB Join, Count 102 and Count 10s see speedup from 1.1x to 1.3x. However, longest 102 and max distance between symbols suffer a slowdown of 0.5x. The structure of these benchmarks is such that transformation to vectorized code increases multiplicative depth and, the negative effect of increased depth is more noticeable in a round-based protocol like GMW. We fix this via a simple heuristic where if the transformation increases circuit depth beyond some threshold (e.g. more than 10\% of the original circuit), we reject the transformation. Nevertheless, we show these graphs here for the sake of completeness and to highlight that vectorization is not always reduce run time. Note that in some settings it may still be desirable to vectorize e.g. in data constrained environments. As shown in \cref{fig:graph_comm_size_time}, vectorization results in reduced communication (i.e. fewer bits are transferred).

We present evaluation for communication size in \cref{fig:graph_comm_size_time}, circuit generation time in \cref{fig:graph_circ_gen_time}, number of gates in \cref{fig:graph_total_gates} and online time and setup time in \cref{fig:graph_online_time} and \cref{fig:graph_setup_time} respectively. \ishaq{Ana: Let me know if I should add more substance.}

- Discuss inner product and biometric in detail on LAN
- Discuss their comparison (Time) with WAN
